Graph Exploration and Search

### 2017-12-24 exploratory.tex
y

Examples have also been used as a mean to detect communities~\citep{staudt2014detecting,perozzi2014focused}, where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node $v \in Q$ as a representative of a different community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the examples.
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns clusters that better represent the seed nodes $Q$.
In addition, FocusCO returns outliers that do not belong to any community identified so far.

@@

A generalization of exemplar queries, PANDA~\citep{xie2017panda}, studies partial topology-based network search. 
That is, to find the connections (paths) between structures node-label isomorphic to different user inputs. 
PANDA first materialize all isomorphic graphs, then groups them into connected components, and finally finds undirected shortest paths among them.

@@

Alternatively, AutoG~\citep{yi2017autog} proposes a top-$k$ reformulation approach for visual autocompletion of queries. 
AutoG returns the $k$ best relaxations according to a ranking function that favors a large number of results for each reformulation and large diversity. 
Such ranking function (excluding normalization) is $u(R) = \alpha \sum_{Q \in R}|\mathcal{R}(Q)|/|\mathcal{D}| + (1-\alpha) \sum_{Q_1, Q_2 \in R} \mathsf{dist}(Q_1, Q_2)$, where  $\alpha \in [0,1]$ strikes a balance between coverage and a user-defined distance $\mathsf{dist}$ among queries.

>>>>

Examples have also been used as a mean to detect communities, 
%~\citep{staudt2014detecting,perozzi2014focused}, 
where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node $v \in Q$ as a representative of a different community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the examples.
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns clusters that better represent the seed nodes $Q$.
FocusCO returns outliers that do not belong to any community identified so far. 
(For community detection, see Chapter ``Community Analytics in Graphs'').

@@

A generalization of exemplar queries, PANDA~\citep{xie2017panda}, studies partial topology-based network search. 
That is, to find the connections (paths) between structures node-label isomorphic to different user inputs. 
PANDA first materialize all isomorphic graphs, then groups them into connected components, and finally finds undirected shortest paths among them. 
More techniques on graph pattern queries are introduced 
in Chapter ``Graph pattern matching'' and 
``Graph query processing''.

@@

Alternatively, AutoG~\citep{yi2017autog} proposes a top-$k$ reformulation approach for visual autocompletion of queries. 
AutoG returns the $k$ best relaxations according to a ranking function that favors a large number of results for each reformulation and large diversity. 
Such ranking function (excluding normalization) is $u(R) = \alpha \sum_{Q \in R}|\mathcal{R}(Q)|/|\mathcal{D}| + (1-\alpha) \sum_{Q_1, Q_2 \in R} \mathsf{dist}(Q_1, Q_2)$, where  $\alpha \in [0,1]$ strikes a balance between coverage and a user-defined distance $\mathsf{dist}$ among queries. For visual query analysis, 
see Chapter ``Visual Graph Querying''.

### 2017-12-24 paper.tex
y

Exploratory methods have been originally introduced as a mean to extract knowledge from relational data without knowing what to search~\citep{idreos2015overview}. 
Recently, \emph{graph exploration} has been introduced to perform exploratory analyses on graph-shaped data~\citep{mottin2017graph}. 
Graph exploration aims at mitigating the access to the data to the user, even if such user is a novice.

Algorithms for graph exploration assume the user is not able to completely specify the object of interest with  a structured query, like a SPARQL~\citep{prud2006sparql} query, but rather expresses the need with a simpler, more ambiguous language.

@@

Keyword search (\kws) has been routinely used to 
explore and understand graph data~\citep{wang2010survey,bao2015exploratory,yahya2016exploratory,mottin2017graph}. 
(1) A keyword query $Q$ is a set of terms $\{t_1, ..., t_n\}$. 
Given graph $G$=$(V, E)$ and a term $t_i$, a match function 
determines a set of {\em content nodes} $V(t_i)\subseteq V$ that match $t_i$. 
(2) An answer 
$G_Q$ of a keyword query $Q$ is a subgraph of $G$ that contains at least 
one node from $V(t_i)$ for each $t_i\in Q$. 
In keyword-based graph exploration, 
a function $F(G_Q)$ is used to quantify the 
cost of connecting all content nodes in $G$. 
Answers with smaller cost have higher quality.

@@

\vspace{.5ex}
\etitle{Distinct root-based KWS}~\citep{kacholia2005bidirectional,he2007blinks}. 
These query defines $G_Q$ as a minimal rooted tree 
which (1) contains a distinct root node $v_r$, and 
at least a content node $v_i\in V(t_i)$ as a leaf for each $t_i\in Q$; 
and (2) $\len(v_r, v_i)\leq r$ for a predefined hop bound $r$, 
for each leaf $v_i$.  Here, $G_Q$ is minimal if 
no subtree of $G_Q$ is an answer of $Q$ in $G$. 
The function $F(G_Q)$ is defined as 
$F(G_Q) = \sum_{t_i\in Q}\dist(v_r, v_i)$, 
where $v_i$ ranges over the content nodes.

The answers of such queries can be found in  
$O(|Q|(|V|\log|V|+|E|))$ time (cf.~\citep{yu2010keyword}).

\etitle{Steiner tree-based KWS}~\citep{bhalotia2002keyword}. 
A Steiner tree-based query differs 
from its distinct root-based counterparts 
in that it uses a different cost function $F(G_Q)$, which is defined as 
$\sum_{e\in G_Q} w(e)$, 
\ie the total weight of the edges in the Steiner tree $G_Q$.

%%%%%%%%%
It is \NP-hard~\citep{yu2010keyword} to evaluate a Steiner tree-based query  
by computing a minimum weighted Steiner tree (\MST, a known \NP-hard problem~\citep{ding2007finding}). 
Both exact~\citep{ding2007finding} and 
approximation algorithms~\citep{byrka2013steiner} 
have been developed to evaluate such queries.

\vspace{.5ex}
\etitle{Steiner graph-based KWS}~\citep{li2008ease,kargar2011keyword}. 
Finding $G_Q$ as graphs rather than trees may be more helpful. For Steiner graph-based queries with a number $r$,  
$G_Q$ is a Steiner graph that contains content and Steiner nodes (\ie nodes 
on shortest paths between two content nodes), with either radius bounded by $r$ 
(\ie r-radius Steiner graph~\citep{li2008ease}), or distance between 
any two content nodes bounded by $r$ (\ie $r$-clique~\citep{kargar2011keyword}). 
For an answer $G_Q$ with nodes $\{v_1, \ldots, v_n\}$,  its cost $F(G_Q)$ 
is computed as  
$\sum_{i\in[1, n]}\sum_{j\in[i+1,n]}\dist(v_i, v_j)$, 
\ie the total pairwise distances of the 
content nodes in $G_Q$. 
Here, the distances are typically 
induced by undirected shortest paths.

It is in general \NP-hard 
to evaluate Steiner graph-based queries~\citep{yu2010keyword, kargar2011keyword}. 
Approximate algorithms are developed for such queries to 
find $r$-radius graphs~\citep{li2008ease}
and $r$-cliques~\citep{kargar2011keyword}.

\stitle{Keyword query suggestion}. 
Keyword query suggestion and its variants 
(\eg query refinement~\cite{mishra2009interactive} and reformulation~\citep{yao2012keyword}) 
have been studied to suggest new queries that better describe search intent 
for graph exploration. 
Most prior work adopts information retrieval techniques that make use of 
query logs and user feedback~\citep{carpineto2012survey,cao2008context}.
Keyword query suggestion for graphs has been studied in ~\citep{tran2009top} by suggesting structured queries computed from the keywords over RDF data. In order to summarize the results of \kws over structured data, tag clouds~\citep{koutrika2009data} discovers the most significant words retrieved as a part of the initial results. 
Provable quality guarantees of the answers are not addressed in these work.

@@

>>>>

Exploratory methods have been introduced as a mean to extract knowledge from relational data without knowing what to search~\citep{idreos2015overview}. 
\emph{Graph exploration} has been introduced to perform exploratory analyses on graph-shaped data~\citep{mottin2017graph}. 
Graph exploration aims at mitigating the access to the data to the user, even if such user is a novice.

Algorithms for graph exploration assume the user is not able to completely specify the object of interest with  a structured query  like a SPARQL %~\citep{prud2006sparql} query, 
(see Chapter ``Graph Query Languages''), 
but rather expresses the need with a simpler, more ambiguous language.

@@

Keyword search (\kws) has been routinely used to 
explore graph data~\citep{wang2010survey,mottin2017graph}. 
(1) A keyword query $Q$ is a set of terms $\{t_1, ..., t_n\}$. 
Given graph $G$=$(V, E)$ and a term $t_i$, a match function 
determines a set of {\em content nodes} $V(t_i)\subseteq V$ that match $t_i$. 
(2) An answer 
$G_Q$ of a keyword query $Q$ is a subgraph of $G$ that contains
a node from $V(t_i)$ for each $t_i\in Q$. 
A function $F(G_Q)$ is used to quantify the 
cost of connecting all content nodes. 
Answers with smaller cost have higher quality.

@@

\vspace{.5ex}
\etitle{Distinct root-based KWS} %~\citep{kacholia2005bidirectional,he2007blinks}. 
defines $G_Q$ as a minimal rooted tree 
which (1) contains a distinct root node $v_r$, and 
at least a content node $v_i\in V(t_i)$ as a leaf for each $t_i\in Q$; 
and (2) $\len(v_r, v_i)\leq r$ for a predefined hop bound $r$, 
for each leaf $v_i$.  Here, $G_Q$ is minimal if 
no subtree of $G_Q$ is an answer of $Q$ in $G$. 
The function $F(G_Q)$ is defined as 
$F(G_Q) = \sum_{t_i\in Q}\dist(v_r, v_i)$, 
where $v_i$ ranges over the content nodes. 
The answers of such queries can be found in  
$O(|Q|(|V|\log|V|+|E|))$ time (cf.~\citep{yu2010keyword}).

\etitle{Steiner tree-based KWS}~\citep{bhalotia2002keyword}. 
differs 
from its distinct root-based counterparts 
in that it uses a different cost function $F(G_Q)$, which is defined as 
$\sum_{e\in G_Q} w(e)$, 
\ie the total weight of the edges in the Steiner tree $G_Q$. 
%%%%%%%%%
It is \NP-hard~\citep{yu2010keyword} to evaluate a Steiner tree-based query  
by computing a minimum weighted Steiner tree, a known \NP-hard problem~\citep{ding2007finding}. 
Both exact~\citep{ding2007finding} and 
approximation algorithms~\citep{byrka2013steiner} 
have been developed to evaluate such queries.

\vspace{.5ex}
\etitle{Steiner graph-based KWS}~\citep{li2008ease,kargar2011keyword} 
finds $G_Q$ as graphs rather than trees. For Steiner graph-based queries with a number $r$,  
$G_Q$ is a Steiner graph that contains content and Steiner nodes (\ie nodes 
on shortest paths between two content nodes), with either radius bounded by $r$ 
(\ie r-radius Steiner graph~\citep{li2008ease}), or distance between 
any two content nodes bounded by $r$ (\ie $r$-clique~\citep{kargar2011keyword}). 
For an answer $G_Q$ with nodes $\{v_1, \ldots, v_n\}$,  its cost $F(G_Q)$ 
is computed as  
$\sum_{i\in[1, n]}\sum_{j\in[i+1,n]}\dist(v_i, v_j)$, 
\ie the total pairwise distances of the 
content nodes in $G_Q$. 
It is in general \NP-hard 
to evaluate Steiner graph-based queries~\citep{yu2010keyword}. 
Approximate algorithms are developed for such queries to 
find $r$-radius graphs~\citep{li2008ease}
and $r$-cliques~\citep{kargar2011keyword}.

\stitle{Keyword query suggestion}. 
Keyword query suggestion and its variants 
(\eg query refinement and reformulation) 
have been studied to suggest new queries that better describe search intent 
for graph exploration. 
Most prior work adopts information retrieval techniques that make use of 
query logs and user feedback~\citep{carpineto2012survey}.
Keyword query suggestion for graphs has been studied in ~\citep{tran2009top} by suggesting structured queries computed from the keywords over RDF data. In order to summarize the results of \kws over structured data, tag clouds~\citep{koutrika2009data} discovers the most significant words retrieved as a part of the initial results. 
Provable quality guarantees of the answers are not addressed in these work.

@@

\section{Cross-References}

\begin{itemize}
\item Graph pattern matching
\item Graph query languages
\item Community analytics in graphs
\item Graph query processing
\item Visual graph querying
\end{itemize}
